The contact value approximation for the pair distribution function of the inhomogeneous hard-sphere fluid

### 2014-06-13 papers/pair-correlation/paper.tex
Added Gil-Villegas approximation to RDF. It needs fixing; there is an m variable, the value of which I could not find. Also, added an alternate version of the RDF plot. Tested on paho-arch. Took 1:13.32.

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{figs/ghs-g2}% \\
  %\includegraphics[width=\columnwidth]{figs/ghs-g-ghs}
  \caption{Plot of the hard-sphere radial distribution function, with
    our separable fit.  The solid lines show the true radial
    distribution function $g(r)$, and the dashed lines show our
    separable fit to the radial distribution functions
    $g_S(r)$.}\label{fig:radial-distribution}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{figs/ghs-g2}% \\
  %\includegraphics[width=\columnwidth]{figs/ghs-g-ghs}
  \caption{Plot of the hard-sphere radial distribution function with our
    separable fit.  The solid lines show the radial distribution function,
    $g(r)$, from MC simulations and the dashed lines show our separable fit
    to the radial distribution function,
    $g_S(r)$.}\label{fig:radial-distribution}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{figs/ghs-alt}
  \caption{Plot of the hard-sphere radial distribution function. The blue
    lines show our separable fit, the black dots are Monte Carlo data, and
    the dashed lines are results of the Gil-Villegas\cite{gil1997statistical}
    fit.\pahosays{An idea for an alternate version of the radial distribution
      figure.}}\label{fig:radial-distribution-alt}
\end{figure}
